R Notebook

### 2021-09-20 documentation_and_analysis/draftbook.Rmd
New car reg vs fuel type

no2_difference <- bind_rows(c(no2_2014, no2_2019))
```

```{r}
# Diff in NO2 between 2014 & 2019
no2_difference <- no2_difference %>% 
  filter(no2 != "MISSING") %>% 
  mutate(no2 = as.numeric(no2),
         year = as.numeric(year)) %>% 
  group_by(x, y) %>% 
  pivot_wider(names_from = "year", values_from = "no2") %>% 
  rename("x2014" = "2014",
         "x2019" = "2019") %>% 
  mutate(no2_diff_2014_2019 = x2014 - x2019) %>% 
#Remove this separation when put in cleaning script
no2_difference <- no2_difference %>% 
  ungroup()
#Remove this separation when put in cleaning script
no2_difference <- no2_difference %>% 
  drop_na()
#Remove this separation when put in cleaning script
# Changing all negative numbers to zero as these aren't of interest to us
no2_difference <- no2_difference %>% 
  mutate(no2_diff_2014_2019 = if_else(no2_diff_2014_2019 < 0, 0, no2_diff_2014_2019))
```

@@

```{r}
ev_charging_rapid <- read_csv(here("raw_data/electric-vehicle-charging-device-statistics-july-2021/EVCD_01b-Table 1.csv"), skip = 6) %>% 
  clean_names() %>% 
  select(la_region_code, local_authority_region_name, apr_21) %>% 
  rename("count_rapid" = apr_21)
ev_charging_total <- read_csv(here("raw_data/electric-vehicle-charging-device-statistics-july-2021/EVCD_01a-Table 1.csv"), skip = 6) %>% 
  clean_names() %>% 
  select(la_region_code, local_authority_region_name, apr_21) %>% 
  rename("count_total" = apr_21)

@@

# Set labels
ev_charging_map_labels <- sprintf(
  "<strong>%s</strong><br/>%g Chargers",
  ev_charging_map$local_authority_region_name.x, ev_charging_map$count_total, ev_charging_map$count_rapid) %>% 
  lapply(htmltools::HTML)
```

```{r}
# Geospatial of EV Total Chargers in the UK April 21
ev_charging_map %>% 
  leaflet() %>% 
  setView(lng = -4.2026, lat = 55.8, zoom = 4.7, options = list()) %>%
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addPolygons(fillColor = ~pal(count_total),
    weight = 0.1,
    opacity = 0.9, 
    color = "black",
    fillOpacity = 0.8,
    highlightOptions = highlightOptions(color = "green", weight = 2,
                                        bringToFront = TRUE),
    label = ev_charging_map_labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>% 
  addLegend(pal = pal, values = ~count_total, opacity = 0.7, title = NULL,
            position = "bottomright")
```

@@

```{r}
# Geospatial of EV Rapid Chargers in the UK April 21
ev_charging_map %>% 
  leaflet() %>% 
  setView(lng = -4.2026, lat = 55.8, zoom = 4.7, options = list()) %>%
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addPolygons(fillColor = ~pal(count_rapid),
    weight = 0.1,
    opacity = 0.9, 
    color = "black",
    fillOpacity = 0.8,
    highlightOptions = highlightOptions(color = "green", weight = 2,
                                        bringToFront = TRUE),
    label = ev_charging_map_labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>% 
  addLegend(pal = pal, values = ~count_rapid, opacity = 0.7, title = NULL,
            position = "bottomright")
```

>>>>

no2_difference <- bind_rows(no2_2014, no2_2019)
```

```{r}
# Diff in NO2 between 2014 & 2019
no2_difference <- no2_difference %>% 
  filter(no2 != "MISSING") %>% 
  mutate(no2 = as.numeric(no2),
         year = as.numeric(year)) %>% 
  group_by(x, y) %>% 
  pivot_wider(names_from = "year", values_from = "no2") %>% 
  rename("x2014" = "2014",
         "x2019" = "2019") %>% 
  mutate(no2_diff_2014_2019 = x2014 - x2019)  %>% 
#Remove this separation when put in cleaning script
  ungroup() %>% 
#Remove this separation when put in cleaning script
  drop_na() %>% 
#Remove this separation when put in cleaning script
# Changing all negative numbers to zero as these aren't of interest to us
  mutate(no2_diff_2014_2019 = if_else(no2_diff_2014_2019 < 0, 0, no2_diff_2014_2019))
```

@@

```{r}
ev_charging_rapid <- read_csv(here("raw_data/electric-vehicle-charging-device-statistics-july-2021/EVCD_01b-Table 1.csv"), skip = 6) %>% 
  clean_names() %>% 
  select(la_region_code, local_authority_region_name, x6) %>% 
  rename("count_rapid" = x6)
ev_charging_total <- read_csv(here("raw_data/electric-vehicle-charging-device-statistics-july-2021/EVCD_01a-Table 1.csv"), skip = 6) %>% 
  clean_names() %>% 
  select(la_region_code, local_authority_region_name, x6) %>% 
  rename("count_total" = x6)

@@

# Set labels
ev_charging_map_labels <- sprintf(
  "<strong>%s</strong><br/>%g Chargers per 100k Population",
  ev_charging_map$local_authority_region_name.x, ev_charging_map$count_total, ev_charging_map$count_rapid) %>% 
  lapply(htmltools::HTML)
```

```{r}
# Geospatial of EV Chargers Per 100k people in the UK April 21
ev_charging_map %>% 
  leaflet() %>% 
  setView(lng = -4.2026, lat = 55.8, zoom = 4.7, options = list()) %>%
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addPolygons(fillColor = ~pal(count_total),
    weight = 0.1,
    opacity = 0.9, 
    color = "black",
    fillOpacity = 0.8,
    highlightOptions = highlightOptions(color = "green", weight = 2,
                                        bringToFront = TRUE),
    label = ev_charging_map_labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>% 
  addLegend(pal = pal, values = ~count_total, opacity = 0.7, title = NULL,
            position = "bottomright")
```

@@

```{r}
# Geospatial of EV Rapid Chargers per 100k people in the UK April 21
ev_charging_map %>% 
  leaflet() %>% 
  setView(lng = -4.2026, lat = 55.8, zoom = 4.7, options = list()) %>%
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addPolygons(fillColor = ~pal(count_rapid),
    weight = 0.1,
    opacity = 0.9, 
    color = "black",
    fillOpacity = 0.8,
    highlightOptions = highlightOptions(color = "green", weight = 2,
                                        bringToFront = TRUE),
    label = ev_charging_map_labels,
    labelOptions = labelOptions(
      style = list("font-weight" = "normal", padding = "3px 8px"),
      textsize = "15px",
      direction = "auto")) %>% 
  addLegend(pal = pal, values = ~count_rapid, opacity = 0.7, title = NULL,
            position = "bottomright")
```

```{r}
uk_ev_map_2021 <- uk_ev_map %>% 
  select(ons_la_code_apr_2019, region_local_authority_apr_2019_3, x2021_q1, geometry)

# filter for desired polygon
highlands <- uk_ev_map_2021 %>% 
  filter(region_local_authority_apr_2019_3 == "Highland")

# st_join seems less dirty
ev_no2 <- final %>% 
  st_as_sf(coords = c("lon", "lat"), crs = st_crs(highlands)) %>% 
  st_join(uk_ev_map_2021, join = st_intersects, left = FALSE) %>% 
  group_by(region_local_authority_apr_2019_3) %>% 
  mutate(mean_no2 = sum(no2))
```

```{r}
ev_no2 %>% 
  ggplot() +
  aes(x = x2021_q1, y = mean_no2) +
  geom_point() +
  geom_smooth(se = TRUE)
```

```{r}
population <- read_csv(here("raw_data/ukpopestimatesmid2020on2021geography/MYE2 - Persons-Table 1.csv"), skip = 7) %>% 
  clean_names() %>% 
  select(code, name, all_ages) %>% 
  mutate(pop_per_100k = all_ages/100000)
```

```{r}
ev_no2_tbl <- tibble(ev_no2) %>% 
  select(-c(no2, geometry)) %>% 
  unique()
```

```{r}
ev_pop_100k <- ev_no2_tbl %>% 
  left_join(population, by = c("ons_la_code_apr_2019" = "code")) %>% 
  mutate(ev_per_100k = x2021_q1/pop_per_100k) 
```

```{r}
ev_pop_100k %>% 
  ggplot() +
  aes(x = ev_per_100k, y = mean_no2) +
  geom_point() +
  geom_smooth(se = TRUE)
```

```{r}
library(cluster)
library(factoextra)
```

```{r}
ev_scale <- ev_pop_100k %>% 
  select(region_local_authority_apr_2019_3, x2021_q1, mean_no2) %>% 
  mutate_if(is.numeric, scale)
```

```{r}
ev_pop_100k_scale <- ev_pop_100k %>% 
  select(region_local_authority_apr_2019_3, ev_per_100k, mean_no2) %>% 
  mutate_if(is.numeric, scale)
```

```{r}
ev_scale %>% 
  ggplot() +
  aes(x = x2021_q1, y = mean_no2) +
  geom_point() +
  geom_smooth(method = lm)
```

```{r}
ev_pop_100k_scale %>% 
  ggplot() +
  aes(x = ev_per_100k, y = mean_no2) +
  geom_point() +
  geom_smooth(method = lm)
```

```{r}
library(corrplot)
```
```{r}
ev_pop_100k_scale %>% 
  as_tibble() %>%
  pivot_longer(-region_local_authority_apr_2019_3,
               names_to = "type", 
               values_to = "value") %>% 
  drop_na() %>% 
  group_by(type) %>%
  summarise(mean = round(mean(value)), 
            sd = sd(value))
```
```{r}
ev_pop_100k_scale_numeric <- ev_pop_100k_scale %>% 
  select(-region_local_authority_apr_2019_3)
```

```{r}
corrplot(cor(ev_pop_100k_scale_numeric), method = "number", type = "lower")
```

```{r}
car_by_fuel_gb <- read_ods(here("raw_data/car_by_fuel_by_year_ALL_UK.ods"), skip = 7) %>% 
  clean_names() %>% 
  head(58) %>% 
  mutate(across(c(petrol:zero_emission8), as.numeric)) %>% 
  filter(petrol >= 100) %>% 
  mutate(traditional_fuel = total - alternative_fuels7 - zero_emission8) %>% 
  select(c("year", "petrol", "diesel", "alternative_fuels7", "zero_emission8")) %>% 
  pivot_longer(cols = c(petrol:zero_emission8), names_to = c("fuel_type"), values_to = c("count"))
```

```{r}
car_by_fuel_gb %>% 
  ggplot() +
  aes(x = year, y = count, colour = fuel_type) +
  geom_smooth(method = lm) +
  geom_point() 
```

```{r}
new_car_by_fuel_gb <- read_ods(here("raw_data/new_car_by_fuel.ods"), skip = 7) %>% 
  clean_names() %>% 
  head(21) %>% 
  mutate(across(c(petrol:zero_emission8), as.numeric)) %>% 
  filter(petrol >= 100) %>% 
  mutate(traditional_fuel = total - alternative_fuels7 - zero_emission8) %>% 
  select(c("date", "petrol", "diesel", "alternative_fuels7", "zero_emission8")) %>% 
  pivot_longer(cols = c(petrol:zero_emission8), names_to = c("fuel_type"), values_to = c("count"))
```

```{r}
new_car_by_fuel_gb %>% 
  ggplot() +
  aes(x = date, y = count, colour = fuel_type) +
  geom_line(aes(group = fuel_type)) +
  theme_minimal() +
  labs(title = "\nNew Car Registrations by Fuel Type\n",
       x = "\nYear\n",
       y = "\nNumber of Cars ('000s)\n",
       colour = "Fuel Type") +
  theme(axis.text.x = element_text(angle = 90, vjust = 0.5, hjust=1)) +
  scale_colour_manual(labels = c("Alternative Fuels", "Diesel", "Petrol", "Zero Emission"), values = c("#abdda4", "#d7191c", "#fdae61", "#2b83ba")) 
```
